Untitled Draft

### 2023-03-15 doc/manuscript.Rmd
Add age categories to demog table

tab <- demog_table |> 
  dplyr::select(Variable = level, Value = out) |> 
  split(demog_table$name)

tab <- append(tab["Numeric variables"], tab[!names(tab) %in% "Numeric variables"])

# Reorder socioeconomic status
tab$`Socioeconomic Status`$Variable <- factor(tab$`Socioeconomic Status`$Variable, levels = c("Low","Medium","High"))
tab$`Sleep Conditions Reported` <- tab$`Sleep Conditions Reported`[tab$`Sleep Conditions Reported`$Variable == "Yes"]
tab$`Socioeconomic Status` <- tab$`Socioeconomic Status`[order(tab$`Socioeconomic Status`$Variable),]

papaja::apa_table(tab, caption = "Participant characteristics",
                  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"))

>>>>

tar_load(demog_table)

papaja::apa_table(demog_table, caption = "Participant characteristics",
                  note = glue::glue("For categorical variables the value is the count, and percentage. For numeric variables the value is the Mean and SD. N = {format(length(unique(table_1$participants$participant_id)),big.mark = ',')}"),
                  landscape = TRUE,
                  col_spanners = list("Age group" = c(2,6)))
